Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2017-04-30 methodology.tex
29-4 10-47

\begin{itemize}
\item Patrones de semanas: Se formaron patrones desde tres semanas continuas
de observación para predecir una semana adelante, hasta doce semanas de
observación para predecir tres semanas adelante. Por tanto, $n\times{}m$, 
with $n=1\ldots{}12$ and $m=1\ldots{}3$.

\item techniques: support vector regression with the kernels linear,
  gaussian and sigmoid; echo state networks; ordinary least squares
  linear regression and elastic-net regression.

\item Variables included in the model:
\begin{itemize}
\item All variables.
\item From the set $\{ \overline{T}_{a} , \overline{H}, P ,
  \overline{W} \}$ use the subsets with one, two, three or four
  elements. These variables have the largest impact on the disease
  development \citep{MarinVargas1995}.
\end{itemize}

\end{itemize}

>>>>

\begin{itemize}
\item Patrones de semanas: Se formaron patrones desde tres semanas continuas
de observación para predecir una semana adelante, hasta doce semanas de
observación para predecir tres semanas adelante. Por tanto, $n\times{}m$ combinations, 
with $n=1\ldots{}12$ and $m=1\ldots{}3$.

\item Techniques: Se utilizaron las siguientes técnicas, revisando el espacio
paramétrico especificado a continuación:
\begin{itemize}
\item SVR with linear kernel: C [0.001, 1, 10, 100, 1000], epsilon [0.0, 0.4, 0.9].
\item SVR with gaussian kernel: C [0.001, 1, 10, 100, 1000], epsilon [0.0, 0.4, 0.9],
gamma [0.0, 0.4, 0.9].
\item SVR with sigmoid kernel: C [0.001, 1, 10, 100, 1000], epsilon [0.0, 0.4, 0.9],
gamma [0.0, 0.4, 0.9], coef0 [0.0, 0.5, 5, 10].
\item Echo state networks: LeakingRate [0.02 .. 0.9], neurons [1\% .. 90\%] de la 
cardinalidad del training set, InitLen [ 0.1 .. 0.8 ].
\item Ordinary least squares linear regression: No parameters.
\item Elastic-net regression: alpha [0 .. 0.9], l1_ratio [0 .. 1.0].
\end{itemize}

\item Variables included in the model:
\begin{itemize}
\item All variables.
\item From the set $\{ \overline{T}_{a} , \overline{H}, P ,
  \overline{W} \}$ use the subsets with one, two, three or four
  elements. These variables have the largest impact on the disease
  development \citep{MarinVargas1995}.
\end{itemize}
\end{itemize}
